Supporting Information: Time Series Modeling of Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-10-30 Ben_Manuscripts/stochastic_transport/Draft.tex
Getting simulations of concentration profiles working

@@

  The evidence suggests that solutes in this system can be well-modeled by 
  subordinated fractional Brownian motion. The solutes clearly perform jumps after periods of relative immobility
  (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM because its analytical correlation 
  structure is close to that observed in our simulation (Figure~\ref{fig:hop_acf}). FBM
  is common in crowded viscoelastic environments where motions are highly influenced by
  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}.

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_trajectories.pdf}
  \caption{}\label{fig:solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{(a) Urea exhibit hops between periods of entrapment, characteristic of a CTRW. 
  (b) The distribution of hop lengths fits well to a Gaussian as well as a more general L\'evy 
  stable distribution. The L\'evy stable distribution does a better job of capturing the 
  heavier tails and increased density near 0. (c) The distribution of dwell times is fit
  well by a power law but it may over-estimate the probability density at long dwell times.
  A power law truncated with an exponential cut-off may better describe the probability of
  long dwell times in our simulations. (d) The hops are negatively correlated to their previous
  hop. In combination (a) -- (d) support modeling solutes as subordinated fractional Brownian
  motion. The behavior shown by urea in this figure is common to all solutes in this study.}\label{fig:anticorrelated_hops}
  %MRS4: are there similar figures in the supporting information.
  %BJC4: no but I can make them
  \end{figure}

  We modeled the distributions of hop lengths in two ways. First, we assumed the 
  distribution to be Gaussian since it is possible to exactly simulate realizations of
  fractional Brownian motion. Second, we fit the distributions to L\'evy stable 
  distributions since it is more general than the Gaussian distribution. We plotted
  the MLE fits of both on top of urea's hop length distribution in 
  Figure~\ref{fig:hop_distribution_comparison}. The L\'evy distribution does a better
  job capturing the heavy tails and high density near 0 of the hop length distribution.
  However, since there are no known exact simulation techniques for generating 
  realizations of fractional L\'evy motion, we must evaluate whether this more general
  fit is worthwhile.

@@

  Using the parameters in Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}
  as inputs to our models, we obtain reasonable predictions of the MD simulated MSDs. The 
  MSD curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs for 
  comparison in Figures~\ref{fig:anomalous_msds_1mode} and Figure~\ref{fig:anomalous_msds_2mode}
  respectively. Our anomalous diffusion trajectories have a significantly reduced 
  uncertainty and lie well within the error bars of MD.

@@

  %BJC3: simulated anomalous diffusion --> SAD ? HMM kind of a downer
  Simulated anomalous diffusion trajectories which draw from a L\'evy stable distribution
  generally predict higher MSDs. The heavy tails of the distribution incorporate large
  jumps more frequently into the trajectories. The only exception is that of ethylene
  glycol in the 2 mode model where the L\'evy index for both modes is near 2, indicating
  a near Gaussian distribution.

  The model parameters for the 1 and 2 mode models tell stories about each solute's behavior. 
  Higher values of $\sigma$ and lower values of $\alpha_h$ indicate larger average 
  hop length magnitudes by increasing the hop length distribution's width and tail 
  density respectively. Higher values of $\alpha_d$ indicate a lower probability of 
  long dwell times. Higher values of $\lambda$ truncate the power law distribution 
  earlier preventing extremely long dwell times. Values of $H$ closer to the Brownian
  limit of 0.5, indicate a lower degree of negative correlation between hops. All 
  of which contribute to an overall increase in the MSD.

  Turning first to the parameters of the 1 mode model, we can begin to break down the
  trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
  relatively similar which is consistent with their similar MD-measured MSDs. Methanol 
  tends to stay trapped for less time and takes larger hops but the most substantial
  difference is with respect to their Hurst parameters. In fact, methanol has the lowest
  $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
  it appears that our model consistently under-predicts the methanol MSD curve relative
  to other solutes. However, it remains plausible that methanol does have a low $H$ 
  value because it spends the majority of its time outside the pore region where collisions
  with tails are frequent. Urea has the third highest MSD which is influenced primarily
  by more frequent and long dwell times, indicated by lower values of $\alpha_d$ and 
  $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
  glycol and methanol. Acetic acid has the smallest MSD among the solutes studied due 
  to longer periods of entrapment and shorter hops. Its trapping behavior is parameterized
  by an $\alpha_d$ value significantly lower than other solutes, but an intermediate 
  $\lambda$ value, suggesting it experiences many medium length periods of entrapment. 
  Its hops are smaller but are slightly compensated by a heavier tailed distribution 
  (lower $\alpha_h$) than the other solutes.

  We can use the 2 mode model to gain an even deeper understanding of solute behavior
  in the pore versus in the tails. It is clear that solutes are significantly slowed 
  while they are in the tail region (mode 2) where long dwell times are more probable
  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Interestingly, 
  $\alpha_h$ for urea and acetic acid in the tails is 1.50 meaning its hop distribution
  is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
  more consistent with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
  structurally similar molecules, both planar with two heavy atoms attached to a 
  carbonyl group. Their small size and rigid shape may allow them to slip through 
  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
  larger jumps to escape traps.

@@

  We further validated our models by training the parameters on half of the 
  equilibrated trajectories and then using them to predict the MSD calculated
  from the alternate half of the trajectories. We trained on both the first
  and second half of the data. At equilibrium, the parameter estimates should 
  be the same, within error, for either portion of the data used for training.

  \begin{table}[h]
  \centering
  \begin{tabular}{|M{1.75cm}|M{1cm}|M{1.65cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|}
  \hline
  \multirow{2}{*}{Solute}&\multirow{2}{*}{Modes}&\multirow{2}{*}{Model}&\multicolumn{2}{c|}{Trained on First Half} & \multicolumn{2}{c|}{Trained on Second Half}        \\\cline{4-7}
                              &                   &        & MD MSD                & Prediction & MD MSD               & Prediction \\\hline
  \multirow{4}{*}{Urea}       & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.43 (1.11, 1.76)}&0.31 (0.28, 0.35)&\multirow{4}{*}{1.43 (1.11, 1.77)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &            &                     &            \\\hline
                              & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.03 (0.79, 1.29)}        &            &\multirow{4}{*}{1.03 (0.77, 1.30)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
  Ethylene                    &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
  Glycol                      &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &            &                     &            \\\hline
  \multirow{4}{*}{Methanol}   &\multirow{2}{*}{1} &sFBMcut&\multirow{4}{*}{1.06 (0.69, 1.36)}        &            &\multirow{4}{*}{1.06 (0.67, 1.37)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
                              &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &            &                     &            \\\hline
  \multirow{4}{*}{Acetic Acid}& \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{0.35 (0.28, 0.45)}&0.31 (0.28, 0.35)&\multirow{4}{*}{0.35 (0.26, 0.47)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &            &                     &            \\\hline
  \end{tabular}
  \caption{}\label{table:sFBM_train}
  \end{table}

@@

  To create an MSDDM for each solute, we generated emission distributions for
  fluctuations within each state and transitions between states. There are not
  enough consecutive observations of each type of transition with which to study
  their individual correlation structures so we grouped all transition distributions
  into a single distribution and measured the correlation of the series of all 
  transitions. We lose information about individual types of transitions, however, 
  we believe this is unavoidable without at least an order of magnitude of additional data.

  We observe correlated emissions drawn from L\'evy stable distributions.
  The deviation of the emission distributions from Gaussian behavior is far more pronounced
  than that seen in the hop length distributions of the previous section, therefore we 
  did not consider the Gaussian case (see Figure~\ref{fig:gaussian_levy_comparison}).
  The correlation structure between hops resembles that of FLM (Figure~\ref{fig:msddm_acf}).
  The parameters of the L\'evy stable distributions along with their Hurst parameters 
  are tabulated in Table~\ref{table:msddm_params}. 
  %MRS4: might this work better visually?  Table in SI, figure here?
  %BJC4: Somehow I'd need to fit 108 pieces of data into a figure
  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
  \caption{}\label{fig:gaussian_levy_comparison}
  \end{subfigure}
  % /figures/msddm_acf.py
  \begin{subfigure}{0.42\textwidth}
  \includegraphics[width=\textwidth]{msddm_acf.pdf}
  \caption{}\label{fig:msddm_acf}
  \end{subfigure}
  \caption{(a) Emission distributions are non-Gaussian and heavy-tailed. Shown here is the
  emission distribution for transitions between states. The maximum likelihood
  Gaussian fit severely underestimates the empirical density of hops near and far from zero 
  while overestimating the density of hops at intermediate values. (b) Jumps drawn from
  the transition distribution are negatively correlated to each other. The normalized version 
  of Equation~\ref{eqn:flm_autocovariance} fits well to the data suggesting FLM is
  an appropriate way to model jumps.} \label{fig:msddm_emissions}
  \end{figure}

>>>>

  %BJC4: Not sure if I should start by commenting on the stationarity of the 
  %solute trajectories. I talk about it when I start validating with the train/test procedure.

%  \subsection{Stationarity of Solute Trajectories}\label{section:stationarity}
%  %BJC4: Maybe re-theme the section: applicability of model
%  
%  Before applying the model, it is important to analyze the MD trajectories
%  themselves in order to understand what conclusions one could reasonably to 
%  draw by applying these models. 
%  
%  %BJC4: this might belong with validation.
%  We observe that in many cases, the distribution of solutes within the membrane
%  evolves slowly with time. We defined the perceived equilibration time point 
%  for each solute based on the time at which the number of solutes inside the
%  pores and tails stabilized. Nonetheless, we observe evidence of non-stationary
%  solute behavior after equilibration on the $\mu$s timescale. In Table \_\_, we compare the MSD of the 
%  solutes calculated using trajectory data from the first and second halves of the
%  equilibrated simulation time. Ethylene glycol and methanol, show considerable
%  differences in their MSDs. Although the MSD calculated from both halves of the 
%  acetic acid trajectories are similar, their shapes are considerably different 
%  (see SI). Urea is the only solute in this study that demonstrates satisfactory
%  stationarity on the 5 $\mu$s timescale.
%  
%  The non-stationary behavior of each solute presents itself in different ways.
%  On average, methanol molecules in the tails appear to be drifting further 
%  away from the pore center with time. Ethylene glycol appears to experience an
%  increased incidence of long trapping times. The partition of acetic acid 
%  between the pores and tails oscillates slowly over time. These problems probably
%  cannot be addressed without more simulation time or additional solute trajectories. 
%  
%  In light of these observations, we chose to demonstrate the performance and insights
%  that could be gained from our models using all of solutes with complete data sets
%  collected after the perceived equilibration time. However, we only use urea to 
%  validate the model's predictive power and to estimate solute flux.
%    
%  There are a couple of ways to address this issue in the long term. The simplest
%  approach is to run the MD simulations longer. This option is likely not feasible
%  because the equilibration timescale in these systems is unknown for most of 
%  the solutes in the study, even after consider computational effort. A more 
%  sustainable approach, which would help screen any solute of interest, would 
%  require us to learn the equilibrium distribution of solutes in the membrane

@@

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. The solutes clearly perform jumps after periods of relative
  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM because its analytical correlation 
  structure is close to that observed in our simulation (Figure~\ref{fig:hop_acf}). FBM
  is common in crowded viscoelastic environments where motions are highly influenced by
  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
  The parameter estimates describing our 1 and 2 mode models are summarized in 
  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}.

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_trajectories.pdf}
  \caption{}\label{fig:solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{(a) Urea exhibit hops between periods of entrapment, characteristic of a CTRW. 
  (b) The distribution of hop lengths fits well to a Gaussian as well as a more general L\'evy 
  stable distribution. The L\'evy stable distribution does a better job of capturing the 
  heavier tails and increased density near 0. (c) The distribution of dwell times is fit
  well by a power law but it may over-estimate the probability density at long dwell times.
  A power law truncated with an exponential cut-off may better describe the probability of
  long dwell times in our simulations. (d) The hops are negatively correlated to their previous
  hop. In combination, (a) -- (d) support modeling solutes as subordinated fractional Brownian
  motion. The behavior shown by urea in this figure is common to all solutes in this study.}\label{fig:anticorrelated_hops}
  %MRS4: are there similar figures in the supporting information.
  %BJC4: no but I can make them
  \end{figure}

  We modeled the distributions of hop lengths in two ways. First, we assumed the 
  distribution to be Gaussian since it is possible to exactly simulate realizations of
  fractional Brownian motion. Second, we fit the distributions to L\'evy stable 
  distributions since it is more general than the Gaussian distribution. We plotted
  the MLE fits of both on top of urea's hop length distribution in 
  Figure~\ref{fig:hop_distribution_comparison}. The L\'evy distribution does a better
  job capturing the somewhat heavy tails and high density near 0 of the hop length distribution.
  However, since there are no known exact simulation techniques for generating 
  realizations of fractional L\'evy motion, we must evaluate whether this more general
  fit is worthwhile.

@@

  Using the parameters in Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}
  as inputs to our models, we obtain reasonable predictions of the MD simulated MSDs. The 
  MSD curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs for 
  comparison in Figures~\ref{fig:anomalous_msds_1mode} and~\ref{fig:anomalous_msds_2mode}
  respectively. 
  %The MSD of AD trajectories modeled using a power law with an exponential 
  %cut-off have a significantly reduced uncertainty and lie well within the error bars of MD.

@@

  Simulated AD trajectories which draw from a L\'evy stable distribution generally 
  predict higher MSDs. The heavy tails of the distribution incorporate large
  jumps more frequently into the trajectories. The only exception is that of ethylene
  glycol in the 2 mode model where the L\'evy index for both modes is near 2, indicating
  a near Gaussian distribution.
  % BJC4: need to explain this somehow.

  The model parameters for the 1 and 2 mode models tell stories about each solute's
  behavior that help explain the difference between the MSDs of different solutes. 
  Higher values of $\sigma$ and lower values of $\alpha_h$ indicate larger average 
  hop length magnitudes by increasing the hop length distribution's width and tail 
  density respectively. Higher values of $\alpha_d$ indicate a lower probability of 
  long dwell times. Higher values of $\lambda$ truncate the power law distribution 
  earlier preventing extremely long dwell times. Values of $H$ closer to the Brownian
  limit of 0.5, indicate a lower degree of negative correlation between hops. All 
  of which contribute to an overall increase in the MSD.

  Turning first to the parameters of the 1 mode model, we can begin to break down the
  trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
  relatively similar which is consistent with their similar MD-measured MSDs. Methanol 
  tends to stay trapped for less time and takes larger hops but the most substantial
  difference is with respect to their Hurst parameters. In fact, methanol has the lowest
  $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
  it appears that our model consistently under-predicts the methanol MSD curve relative
  to other solutes. However, it remains plausible that methanol does have a low $H$ 
  value because it spends the majority of its time outside the pore region where collisions
  with tails are frequent. Urea has the third highest MSD that is primarily a consequence of
  more frequent and long dwell times, indicated by lower values of $\alpha_d$ and 
  $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
  glycol and methanol. Acetic acid has the smallest MSD among the solutes studied due 
  to longer periods of entrapment and shorter hops. Its trapping behavior is parameterized
  by an $\alpha_d$ value significantly lower than other solutes, but an intermediate 
  $\lambda$ value, suggesting it experiences many medium length periods of entrapment. 
  Its hops are smaller but are slightly compensated by a heavier tailed distribution 
  (lower $\alpha_h$) than the other solutes.

  We can use the 2 mode model to gain an even deeper understanding of solute behavior
  in the pore versus in the tails. It is clear that solutes are significantly slowed 
  while they are in the tail region (mode 2) where long dwell times are more probable
  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Interestingly, 
  $\alpha_h$ for urea and acetic acid in the tails is 1.50 meaning its hop distribution
  is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
  more consistent with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
  structurally similar molecules, both planar with two heavy atoms attached to a 
  carbonyl group. Their small size and rigid shape may allow them to occasionally slip
  through gaps in the tails. Meanwhile, methanol is small enough that it does not need
  to make larger jumps to escape traps.

@@

  \subsubsection{Model validation on stationary trajectories}\label{section:sfbm_validation}

  We evaluated the predictive capabilities of the AD modeling approach by training
  the model parameters on the first half of the equilibrated MD trajectory data
  then comparing the MSD calculated from AD model realizations to the MSD calculated
  from the second half of the equilibrated MD trajectory data. This metric is
  only meaningful if the ensemble of solute trajectories is stationary.

  We observe that in many cases, the distribution of solutes within the membrane
  evolves slowly with time. We defined the perceived equilibration time point 
  for each solute based on the time at which the number of solutes inside the
  pores and tails stabilized. Nonetheless, we observe evidence of non-stationary
  solute behavior after equilibration, on the $\mu$s timescale. In Table~\ref{table:stationarity},
  we compare the MSD of the solutes calculated using trajectory data from the 
  first and second halves of the equilibrated simulation time. Ethylene glycol 
  and methanol show considerable differences in their MSDs. Urea and acetic acid
  appear to demonstrate satisfactory stationarity on the 5 $\mu$s timescale. The
  shapes of their MSDs curves are also very similar (see Figure~\ref{S-fig:msd_comparison}
  of the Supporting Information).

  \begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|}
  \hline
  \multirow{2}{*}{Residue} & \multicolumn{2}{c|}{MSD}            \\\cline{2-3}
                           & First Half       & Second Half      \\\hline
  Urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
  Ethylene Glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
  Methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
  Acetic Acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline

  \end{tabular}
  \caption{In order to be considered stationary, the MSD of the ensemble of solute trajectories
  should be the same independent of the portion of equilibrated trajectory that is
  analyzed. The MSD values in this table are averages taken after a 500 ns time lag, 
  calculated independently from the first and second halves of the equilibrated
  solute trajectories. Urea and acetic acid both appear to satisfy the stationarity
  criteria, while ethylene glycol and methanol show significantly smaller MSDs 
  when calculated from the second half of the equilibrated trajectories.}\label{table:stationarity}
  \end{table}

  The non-stationary behavior of ethylene glycol and methanol present themselves
  in different ways. On average, methanol molecules in the tails appear to be 
  drifting further away from the pore center with time. Methanol's small size 
  significantly increases the volume of accessible structural space. Ethylene 
  glycol appears to experience an increased incidence of long trapping times. 
  These problems probably cannot be addressed without more simulation time or 
  additional solute trajectories.

  Using the approach described above, we validated our 1 and 2 mode models with
  urea and acetic acid, since their trajectories appear stationary. The 
  resultant MSD plots are shown in Figure~\ref{fig:train_test}.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (1 mode)}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (2 modes)}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (1 mode)}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (2 modes)}
  \end{subfigure} 
  \caption{The MSD curves predicted by the AD model trained on the first half 
  of the equilibrated data closely reproduce the MSD curves generated from the 
  second half of the equilibrated solute data.}\label{fig:train_test}
  \end{figure}

  The models reasonably predict the MSD of the second half of the solute 
  trajectories based on parameters generated from the first half. This success
  provides increased confidence in our ability to generate useful predictions
  of long time scale solute behavior

%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|M{1.75cm}|M{1cm}|M{1.65cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|}
%  \hline
%  \multirow{2}{*}{Solute}&\multirow{2}{*}{Modes}&\multirow{2}{*}{Model}&\multicolumn{2}{c|}{Trained on First Half} & \multicolumn{2}{c|}{Trained on Second Half}        \\\cline{4-7}
%                              &                   &        & MD MSD                & Prediction & MD MSD               & Prediction \\\hline
%  \multirow{4}{*}{Urea}       & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.43 (1.11, 1.76)}&0.31 (0.28, 0.35)&\multirow{4}{*}{1.43 (1.11, 1.77)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
%                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
%                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
%                              &                   &sFLMcut&                         &            &                     &            \\\hline
%                              & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.03 (0.79, 1.29)}        &            &\multirow{4}{*}{1.03 (0.77, 1.30)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
%  Ethylene                    &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
%  Glycol                      &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
%                              &                   &sFLMcut&                         &            &                     &            \\\hline
%  \multirow{4}{*}{Methanol}   &\multirow{2}{*}{1} &sFBMcut&\multirow{4}{*}{1.06 (0.69, 1.36)}        &            &\multirow{4}{*}{1.06 (0.67, 1.37)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
%                              &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
%                              &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
%                              &                   &sFLMcut&                         &            &                     &            \\\hline
%  \multirow{4}{*}{Acetic Acid}& \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{0.35 (0.28, 0.45)}&0.31 (0.28, 0.35)&\multirow{4}{*}{0.35 (0.26, 0.47)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
%                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
%                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
%                              &                   &sFLMcut&                         &            &                     &            \\\hline
%  \end{tabular}
%  \caption{}\label{table:sFBM_train}
%  \end{table}

@@

  To create an MSDDM for each solute, we determined the state sequence of each 
  solute solute trajectory and then generated emission distributions for fluctuations
  within each state as well as transitions between states. There are not enough 
  consecutive observations of each type of transition with which to study their 
  individual correlation structures so we grouped all transition distributions
  into a single distribution and measured the correlation of the series of all 
  transitions. We lose information about individual types of transitions, however, 
  we believe this is unavoidable without at least an order of magnitude of additional data.

  We observe correlated emissions drawn from L\'evy stable distributions. The 
  deviation of the emission distributions from Gaussian behavior is far more pronounced
  than that seen in the hop length distributions of the previous section, therefore we 
  did not consider the Gaussian case (see Figure~\ref{fig:gaussian_levy_comparison}).
  The correlation structure between hops resembles that of FLM (Figure~\ref{fig:msddm_acf}).
  The parameters of the L\'evy stable distributions along with their Hurst parameters 
  are tabulated in Table~\ref{table:msddm_params}.

  %MRS4: might this work better visually?  Table in SI, figure here?
  %BJC4: Are you talking about the table after this figure? Somehow I'd need to fit 108 pieces of data into a single figure
  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
  \caption{}\label{fig:gaussian_levy_comparison}
  \end{subfigure}
  % /figures/msddm_acf.py
  \begin{subfigure}{0.42\textwidth}
  \includegraphics[width=\textwidth]{msddm_acf.pdf}
  \caption{}\label{fig:msddm_acf}
  \end{subfigure}
  \caption{(a) Emission distributions are non-Gaussian and heavy-tailed. Shown here is the
  emission distribution for transitions between states. The maximum likelihood
  Gaussian fit severely underestimates the empirical density of hops near and far from zero 
  while overestimating the density of hops at intermediate values. (b) Jumps drawn from
  the transition distribution are negatively correlated to each other. The normalized version 
  of Equation~\ref{eqn:flm_autocovariance} fits well to the data suggesting FLM is
  an appropriate way to model jumps.} \label{fig:msddm_emissions}
  \end{figure}

### 2019-10-30 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Getting simulations of concentration profiles working

@@

>>>>

  \section{Stationarity of Solute Trajectories}\label{section:msd_comparison}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
  \caption{Urea}\label{fig:URE_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
  \caption{Methanol}\label{fig:MET_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
  \end{subfigure}
  \caption{The ensemble of solute trajectories may be stationary if the MSD
  calculated from different portions of the trajectory are the same. Here we
  plot the MSD calcluated up to a 500 ns time lag of the first and second
  halves of the equilibrated solute trajctories. Urea and acetic acid have
  similar MSDs, providing evidence of stationarity, while the MSDs of 
  ethylene glycol and methanol are different.}\label{fig:msd_comparison}
  \end{figure}

@@

  \section{Mean first passage time simulations}\label{section:mfpt}

  We validated our approach to simulating trajectory realizations by testing
  it against analytical solutions to the mean first passage time of a Brownian
  particle with 2 absorbing boundaries.

  % equations here 
  % Analytical CDF: https://journals.aps.org/pre/pdf/10.1103/PhysRevE.73.046104
  % Analytical MFPT https://journals.aps.org/pre/pdf/10.1103/PhysRevE.62.6065
  % Figures: mfpt_pdf.pdf and mfpt_cdf.pdf
